Comparing Early Evolution of Flames in X-ray Bursts in Two and Three Dimensions

### 2023-05-17 xrb3/paper.tex
archive
start addressing referee

\documentclass[twocolumn,linenumbers,times,tighten]{aastex631}

\usepackage{epsf,color,amsmath}

\usepackage{cancel}

@@

\begin{figure}[t]
\centering
%\epsscale{0.75}
\plotone{abar_top_stack}
%\epsscale{1.0}
\caption{\label{fig:vr_abar} Volume rendering of the three-dimensional XRB
simulation showing the mean molecular weight, $\bar{A}$.  The flame is viewed
from above. The panels show the state at 10 ms, 20 ms, and 40 ms (from top to bottom).}
\end{figure}

>>>>

\documentclass[linenumbers]{aastex631}

%\usepackage{xcolor,amsmath}

\usepackage[T1]{fontenc}

@@

\begin{figure}[t]
\centering
\plotone{full}
\caption{\label{fig:vr_abar} Volume rendering of the three-dimensional XRB
simulation showing the mean molecular weight, $\bar{A}$.  Two views
are shown: the left column is viewed from above while the right column
shows it from a shallow angle above the surface.  The panels show the state at 10 ms, 20 ms, and 40 ms (from top to bottom).
The colorbar shows the value of $\bar{A}$ together with the opacity assigned for
that value---this allows us to bring out some structure in the rendering.  A
small triad in the upper right of the top panels shows the orientation,
with red = $x$, green = $y$, and blue = $z$, our vertical direction.}
\end{figure}
